---
title: 'Assignment: R Markdown & Leaflet'
author: "N. Lakhani"
date: "29 January 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive Summary


This report creates a web page featuring a map created with Leaflet. The webpage is hosted on RPubs and my GitHub page. As required, the map includes

* an interactive map showing the cities I have visited


### Customize map & render

This section defines

* creates map frame using Leaflet
* populates it usign tiles and data provided in a dataframe - which includes all countries I have visited
* renders the map below 


```{r echo=FALSE,warning=FALSE,message=FALSE}

library(leaflet)
library(dplyr)

df <- data.frame (lat=c(46,56,55,3,22.39,32,39,24,38,13,26,25,20,51,41,50,51),lng=c(2.2,-106,3.4,101,39,-97,21,46,35,103,30,55,78,10,12,4.4,19))
myvisit <- c('France','Canada','UK','Malaysia','Hong Kong','Dallas','Greece','Saudi Arabia','Turkey','Singapore','Eygpt','Dubai','Delhi','Germany','Italy','Belgium','Poland')
my_map <- df %>% leaflet() %>% addTiles() %>% addMarkers(popup=myvisit)      
                                               
 

my_map

```

