---
title: "Predicting Iris Species - Coursera Project"
author: "Narinder Lakhani"
date: "2 February 2018"
transition: fade
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=TRUE,echo=FALSE }
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE,eval=FALSE)

```


## Executive Summary

The objective of this project is to create the following:

* A small application using the **Shiny** package
* The application prompts user inputs for specific variables (which are also used in building the model) and predicts **Iris Species** using the **Rpart** model

## Overview of the Application

The following steps are followed in the Shiny application created: 

* Load Iris data
* Build the prediction model using the a) **Caret** package b) method **rpart** and, c) Iris dataset
* The model is built using all variables in the iris dataset (formula: Species ~.). So, not be a completely optimized model

```{r,eval=FALSE}
library(caret)
library(rpart.plot)
library(rattle)
data(iris)
fit <- train (Species ~.,data=iris,method='rpart')
```

## Application: Inputs and Output

* The Shiny application accepts Petal Length, Petal Width, Sepal Length and Sepal Width from the user. The user is prompted to press **submit** after the input is entered 
* The app constructs a new data frame from user inputs for the predict function of the model created
* The application finally outputs the predicted **Species** and the classification tree used to arrive at the Species prediction 


```{r echo = TRUE}
userInput <- data.frame(4.5,2.0,4.3,2.5)
names(userInput)<-c("Sepal.Width","Petal.Length", "Petal.Width","Sepal.Length")
predict(fit,newdata=userInput)
fancyRpartPlot(fit$finalModel)


```

